---
title: "Presidential Debate Tone Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Overview

The following is an analysis of the Presidential Debate speeches using IBM's Tone Analyzer API from Watson Analytics, Python and R. 

First, we connect to website with the transcripts of the presidential debate, and using regular expressions, mine for those words that were spoken by each candidate during the debate.

```{python}

import urllib.request
URL = 'http://www.politico.com/story/2016/10/2016-presidential-debate-transcript-229519'

def getWebpage(theURL):
    response = urllib.request.urlopen(theURL)
    html = response.read()
    html = html.decode()
    print("got it!")
    f = open('debatetext.txt', 'w')
    f.write(html)
    f.close()
    print("all done!")    
    
getWebpage(URL) 

#use regular expressions to parse out clinton and trump text and join them into one string
import re
data = open(r'debatetext.txt','r').read()
print(len(data))
clinton = re.findall(r'(?<=<b>Clinton<\/b>:)(.*)(?=</p>)', data, re.MULTILINE)
trump = re.findall(r'(?<=<b>Trump<\/b>:)(.*)(?=</p>)', data, re.MULTILINE)
clinton = [''.join(clinton[0:len(clinton)])]
trump = [''.join(trump[0:len(trump)])]
print(len(clinton), len(trump))
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
